Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-12 paper.tex

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/cophylogeny_wide.pdf}
\caption{\label{fig:cophlogeny} DESCRIBE ME.
}
\end{figure}

Figure~\ref{fig:cophlogeny} shows a co-phylogeny of the 88 samples shared between the wide ARG and
a GISAID global "all-time" tree from NextStrain (downloaded on January 21,
2023). To reduce the ARG to a single tree, we show the very first tree in the
wide ARG; however, the five other trees in this simplified ARG show
near-identical patterns. Supplementary Figure 3 shows the same comparison for
the long ARG. It is clear that the backbone topology of the sc2ts tree shows
very close agreement with the NextStrain tree. The sample genomes cluster by
their assigned Pango lineage status, and many variants and their descendents
form identical monophyletic clades in both the trees (e.g., the Alpha and Delta
clades).

@@

@@

\section{Supplementary}

@@

>>>>

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/cophylogeny_wide.pdf}
\caption{\label{fig:cophylogeny} DESCRIBE ME. See
Figure~\ref{fig:cophlogeny_long} for the equivalent cophylogeny
for the Long ARG.
}
\end{figure}

Figure~\ref{fig:cophylogeny} shows a co-phylogeny of the 88 samples shared between the wide ARG and
a GISAID global "all-time" tree from NextStrain (downloaded on January 21,
2023). To reduce the ARG to a single tree, we show the very first tree in the
wide ARG; however, the five other trees in this simplified ARG show
near-identical patterns. Supplementary Figure 3 shows the same comparison for
the long ARG. It is clear that the backbone topology of the sc2ts tree shows
very close agreement with the NextStrain tree. The sample genomes cluster by
their assigned Pango lineage status, and many variants and their descendents
form identical monophyletic clades in both the trees (e.g., the Alpha and Delta
clades).

@@

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/recombination_node_mrcas.pdf}
\caption{\label{fig:recomb_mrcas} Divergance between parents at
recombination breakpoints. (A) All recombination nodes that are ancestral
to least two samples. (B) Further filtered as described in the text.
MORE DETAIL. Horizontal lines represent WHAT,
Figure~\ref{fig:recomb_mrcas_lineage_breakdown} shows the same data
broken down by parental lineage.}
\end{figure}

@@

\renewcommand\thefigure{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand\thetable{S\arabic{table}}
\setcounter{table}{0}
\section*{Supplementary}

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/supp_cophylogeny_long.pdf}
\caption{\label{fig:cophlogeny_long}Copyhlogeny for the Long ARG. MORE DETAIL.}
\end{figure}

@@

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/supp_recombination_node_mrcas.pdf}
\caption{\label{fig:recomb_mrcas_lineage_breakdown}  DESCRIBE ME}
\end{figure}
